Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-22 doc/PRF2022/Supplementary.tex

\section{Movie Captions}\mbox{} \\

\noindent
{\bf Movie S1. Relaxation} 
There are 60 circular particles with radius 1.25~nm that are initially
confined in a square box. The simulation results show the relaxation
with each of the three boundary conditions. The time step of all
simulations is $\Delta t=0.2$. The color on the boundary from blue to
red is for $\min g(\xx)$ to $\max g(\xx)$. All final configurations are
adopted in simulations with hydrodynamic flows. \\

\noindent
{\bf Movie S2. Structures in a Shear Flow without Ruptures} 
We adopt the relaxed configurations and place the JP structures in the
shear flow. For the choices of the shear rate, we pick: $\dot\gamma =
0.05$ for the vesicle, $\dot\gamma = 0.05$ for the bilayer, $\dot\gamma
= 0.05$ for the multi-lamellar, and $\dot\gamma = 0.1$ for the striated
configurations. The vesicle case undergoes tank-treading whereas the
initially disordered BC (i) case increases orientational order. The
multilamellar assemply behaves as a rigid body, and the striated
configuration moreso. No ruptures occur. \\

\noindent
{\bf Movie S3. Structures in a Taylor-Green Flow without Ruptures} 
We adopt the relaxed configurations and place the JP structures in the
Taylor-Green flow at low flow rates. For the choices of the flow
strength, we pick: $V_0 = 0.1$ for the vesicle, $V_0 = 0.1$ for the
disordered bilayer, $V_0 = 0.1$ for the multi-lamellar, and $V_0 = 0.2$
for the striated configurations. The vesicle stays inact, whereas the
dissordered bilayer is pulled apart. Like in Supplementary Movie S2, the
striated assembly is basically rigid. \\

\noindent
{\bf Movie S4. Structures in a Shear Flow with Ruptures} 
We adopt the relaxed configurations and place the JP structures in the
shear flow at a higher shear rate. For the choices of the shear rate, we
pick: $\dot\gamma = 0.075$ for the vesicle, $\dot\gamma = 0.1$ for the
bilayer, $\dot\gamma = 0.15$ for the multi-lamellar, and $\dot\gamma =
0.15$ for the striated configurations. The time step of all simulations
is $\Delta t=0.2$. In this movie, some clear structural ruptures occur
in each case. In order to observe the structure behaviors at later time,
we stabilize the frame by tracking the center of mass position of all
JP. \\

\noindent
{\bf Movie S5. Structures in a Taylor-Green Flow with Ruptures} 
We adopt the relaxed configurations and place the JP structures in the
Taylor-Green flow at higher flow rates. For the choices of the flow
strength, we pick: $V_0 = 0.2$ for the vesicle, $V_0 = 0.2$ for the
bilayer, $V_0 = 0.2$ for the multi-lamellar, and $V_0 = 0.3$ for the
striated configurations. Clear structural ruptures occur in each case.
In all cases, there is significant reduction in the orientational order
of the assemblies. While the BC (i) cases are broken into several
pieces, the main body of the BC (ii) and BC (iii) assemblies are not
pulled apart by the background flow.

\section{Raw Data}
The following figures plot the fully resolved simulation time-courses
organized in terms of the bilayer, vesicle BL, multilamellar, and striated JP phases
under shear flow (Supplementary Figures~\ref{fig:ulshraw}--\ref{fig:stshraw})
and under TG flow (Supplementary Figures~\ref{fig:ultgraw}--\ref{fig:sttgraw}).
Throughout, panels (a) are for relative free energy $F - F_0$,
panels (b) for alignment $S_2$, and panels (c) for strain $E$ (as a percentage). 
A common ordinate is used for each of the respective panels to facilitate
comparison between data sets. 
\newpage

>>>>

\section{Movie Descriptions}
We consider suspensions of JPs of radius 1.25~nm. The time step size for
all simulations is $\Delta t = 0.2$~ns. The colors of the JPs are as
follows: for Type I and Vesicles, red is hydrophobic ($\max g > 0$) and
blue is hydrophilic ($\min g = 0$); for Type II, red is more hydrophobic
($\max g >0$) than blue ($\min g > 0$); for Type III, red is positively
charged ($\max g > 0$) and blue is negatively charged ($\min g < 0$).
%\mbox{} \\

\noindent
{\bf Relaxation}: The relaxation of 60 circular JPs that are initialized
with random locations and orientations. The JPs self-assemble into
unilamellar (Type I), multilamellar (Type II), and striated (Type III)
configurations. The final configurations are used as initial conditions
for the simulations that include a background flow.

%There are 60 circular particles with radius 1.25~nm that are initially
%confined in a square box. The simulation results show the relaxation
%with each of the three boundary conditions. The time step of all
%simulations is $\Delta t=0.2$. The color on the boundary from blue to
%red is for $\min g(\xx)$ to $\max g(\xx)$. All final configurations are
%adopted in simulations with hydrodynamic flows. \\

\noindent
{\bf Structures in a Weak Shear Flow}:
The relaxed configurations of the 60 JPs are subjected to a weak shear
flow. The shear rate is $\dot{\gamma} = 0.05$~ns$^{-1}$ for the Vesicle,
Type I, and Type II configurations, and $\dot{\gamma} = 0.1$~ns$^{-1}$
for the Type III configuration. The vesicle undergoes tank-treading and
the bilayer increases its orientational order. The multilamellar
configuration resembles a rigid body motion, and the striated
configuration has an even stronger resemblance to a rigid body motion.
No ruptures occur in these examples.

%We adopt the relaxed configurations and place the JP structures in the
%shear flow. For the choices of the shear rate, we pick: $\dot\gamma =
%0.05$ ns$^{-1}$ for the vesicle, $\dot\gamma = 0.05$ ns$^{-1}$ for the
%bilayer, $\dot\gamma = 0.05$ ns$^{-1}$ for the multi-lamellar, and
%$\dot\gamma = 0.1$ ns$^{-1}$ for the striated configurations. The
%vesicle case undergoes tank-treading whereas the initially disordered
%BC (i) case increases orientational order. The multilamellar assemply
%behaves as a rigid body, and the striated configuration moreso. No
%ruptures occur. \\

\noindent
{\bf Structures in a Weak Taylor-Green Flow}:
The relaxed configurations of the 60 JPs are subjected to a weak
Taylor-Green flow. The flow rate is $\dot{\gamma} = 0.05$~ns$^{-1}$ for
the Vesicle, Type I, and Type II configurations, and $\dot{\gamma} =
0.1$~ns$^{-1}$ for the Type III configuration. The vesicle stays intact,
whereas the bilayer is pulled apart into different TG cells. Like in the
weak shear flow example, the multilamellar and striated configurations
behave as rigid bodies.

%For the choices of the flow strength, we pick: $\dot\gamma = 0.05$
%ns$^{-1}$ for the vesicle, $\dot\gamma = 0.05$ ns$^{-1}$ for the
%disordered bilayer, $\dot\gamma = 0.05$ ns$^{-1}$ for the
%multi-lamellar, and $\dot\gamma = 0.1$ ns$^{-1}$ for the striated
%configurations. The vesicle stays inact, whereas the dissordered
%bilayer is pulled apart. Like in Supplementary Movie S2, the striated
%assembly is basically rigid. \\

%We adopt the relaxed configurations and place the JP structures in the
%Taylor-Green flow at low flow rates. For the choices of the flow
%strength, we pick: $\dot\gamma = 0.05$ ns$^{-1}$ for the vesicle,
%$\dot\gamma = 0.05$ ns$^{-1}$ for the disordered bilayer, $\dot\gamma =
%0.05$ ns$^{-1}$ for the multi-lamellar, and $\dot\gamma = 0.1$
%ns$^{-1}$ for the striated configurations. The vesicle stays inact,
%whereas the dissordered bilayer is pulled apart. Like in Supplementary
%Movie S2, the striated assembly is basically rigid. \\

\noindent
{\bf Structures in a Strong Shear Flow}:
The relaxed configurations of the 60 JPs are subjected to a strong shear
flow. The shear rate is $\dot{\gamma} = 0.075$~ns$^{-1}$ for the Vesicle
configuration, $\dot{\gamma} = 0.1$~ns$^{-1}$ for the Type I
configuration, and $\dot{\gamma} = 0.15$~ns$^{-1}$ for the Type II and
Type III configurations. In all cases, the structure is ruptured by the
flow. The frames are stabilized by moving with the center of mass of all
the JPs.

%We adopt the relaxed configurations and place the JP structures in the
%shear flow at a higher shear rate. For the choices of the shear rate, we
%pick: $\dot\gamma = 0.075$ for the vesicle, $\dot\gamma = 0.1$ ns$^{-1}$
%for the bilayer, $\dot\gamma = 0.15$ ns$^{-1}$ for the multi-lamellar,
%and $\dot\gamma = 0.15$ ns$^{-1}$ for the striated configurations. The
%time step of all simulations is $\Delta t=0.2$ ns$^{-1}$. In this movie,
%some clear structural ruptures occur in each case. In order to observe
%the structure behaviors at later time, we stabilize the frame by
%tracking the center of mass position of all JP. \\

\noindent
{\bf Structures in a Strong Taylor-Green Flow}:
The relaxed configurations of the 60 JPs are subjected to a strong
Taylor-Green flow. The flow rate is $\dot{\gamma} = 0.1$~ns$^{-1}$ for
the Vesicle, Type I, and Type II configurations, and $\dot{\gamma} =
0.15$~ns$^{-1}$ for the Type III configuration. In all cases, the
structure is ruptured by the flow and there is a significant reduction
in the orientation order. While the Vesicle Type I configurations are
broken into several pieces, the main body of the Type II and Type III
configurations are not pulled apart by the background flow.

%We adopt the relaxed configurations and place the JP structures in the
%Taylor-Green flow at higher flow rates. For the choices of the flow
%strength, we pick: $\dot\gamma = 0.1$ ns$^{-1}$ for the vesicle, $\dot\gamma = 0.1$ ns$^{-1}$ for the
%bilayer, $\dot\gamma = 0.1$ ns$^{-1}$ for the multi-lamellar, and $\dot\gamma = 0.15$ ns$^{-1}$ for the
%striated configurations. Clear structural ruptures occur in each case.
%In all cases, there is significant reduction in the orientational order
%of the assemblies. While the BC (i) cases are broken into several
%pieces, the main body of the BC (ii) and BC (iii) assemblies are not
%pulled apart by the background flow.\\

\noindent
%{\label{MovieS6}\bf JP Vesicle in a Taylor-Green Flow with Various
%$\lambda$ Values}: 
{\label{MovieS6}\bf JP Vesicle in Various Taylor-Green Flows}: A
circular vesicle bilayer is placed in a Taylor-Green flow. The parameter
$\lambda$ controls the TG cell size and the values are varied from 1~nm
to 4~nm while the flow rate is chosen so that
$\lambda\dot\gamma=0.1$~nm/ns. The parameter $\lambda$ determines the
steady-state polygonal tank-treading shape. The rotation direction is
clockwise for $\lambda=1$~nm and $\lambda=2$~nm, and counterclockwise
for $\lambda=3$~nm and $\lambda=4$~nm. Streamlines of the flow are
included.

%A circular vesicle bilayer is placed in the Taylor-Green flow.  The
%parameter $\lambda$ controls the cell size and the values are varied
%from 1.0 nm to 4.0 nm while the flow rate $\lambda\dot\gamma=0.1$ is
%fixed. There is a rotation transition from clockwise ($\lambda=1$ nm and
%2 nm) to counterclockwise ($\lambda=3$ nm and 4 nm). Moreover, the
%resulting steady shapes of all cases are different polygons. We plot the
%streamlines in the background.\\

\section{Raw Data}
The following figures plot the fully resolved simulation time-courses
organized in terms of the bilayer, vesicle BL, multilamellar, and striated JP phases
under shear flow (Supplementary Figures~\ref{fig:ulshraw}--\ref{fig:stshraw})
and under TG flow (Supplementary Figures~\ref{fig:ultgraw}--\ref{fig:sttgraw}).
Throughout, panels (a) are for relative free energy $F - F_0$,
panels (b) for alignment $S_2$, and panels (c) for strain $E$ (as a percentage). 
A common ordinate is used for each of the respective panels to facilitate
comparison between data sets. 
%\newpage
